Estimating Predictive Rate-Distortion Curves via Neural Variational Inference

### 2019-06-12 paper.tex
revising

\subsection{Related Work}
In (\ref{eq:bound}), we derived a variational formulation of predictive rate-distortion.
This is formally related to a variational formulation of the Information Bottleneck that was introduced by \cite{alemi-deep-2016}, who applied it to neural-network based image recognition.
Unlike our approach, they used a fixed diagonal Gaussian instead of a flexible parametrized distribution for $q$.
As far as we are aware, no previous work has used such a variational formulation in the modeling of sequences.

In the neural networks literature, the most commonly used method using variational bounds similar to (\ref{eq:bound}) is the Variational Autoencoder \citep{kingma-auto-encoding-2014, bowman-generating-2016}, which corresponds to the setting where $\lambda=1$ and the predicted output is equal to the observed input.

%More broadly, our method is related to  The idea will be to use Variational Inference~\citep{blei-variational-2016}:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{We thank Dan Jurafsky for helpful discussion.}

>>>>

\subsection{Related Work}
In (\ref{eq:bound}), we derived a variational formulation of predictive rate-distortion.
This is formally related to a variational formulation of the Information Bottleneck that was introduced by \cite{alemi-deep-2016}, who applied it to neural-network based image recognition.
Unlike our approach, they used a fixed diagonal Gaussian instead of a flexible parametrized distribution for $q$.
%As far as we are aware, no previous work has used such a variational formulation specifically .
Some recent work has applied similar approaches to the modeling of sequences, employing models corresponding to the objective~(\ref{eq:bound}) with $\lambda=1$~\citep{grathwohl2016disentangling,walker2016uncertain,fraccaro2017disentangled,hernandez2018variational}.

In the neural networks literature, the most commonly used method using variational bounds similar to (\ref{eq:bound}) is the Variational Autoencoder \citep{kingma-auto-encoding-2014, bowman-generating-2016}, which corresponds to the setting where $\lambda=1$ and the predicted output is equal to the observed input.
The $\beta$-VAE \citep{higgins2017beta}, a variant of the Variational Autoencoder, uses $\lambda > 1$ (whereas the Predictive Rate-Distortion objective~(\ref{eq:ib}) uses $\lambda \in (0,1)$), and has been linked to the Information Bottleneck by \cite{burgess2018understanding}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{We thank Dan Jurafsky for helpful discussion, and the anonymous reviewers for helpful comments.}
